%\glsresetall

The project \gls{odina} focuses on the process-based modeling of ozone induced damage on vegetation. To this end the applicant will implement a two-way coupling of ozone between the atmosphere and land-biosphere in a widely used global \gls{ccm}, the \gls{cesm}. \textbf{\gls{odina} studies the vegetations' feedback on near-surface to tropospheric ozone concentrations and will improve our process-level understanding of dry deposition effects on air quality and plant health.} The improved capabilities of \gls{cesm} including the \gls{odina} model will be demonstrated and effects of air quality regulations, and biosphere feedbacks on surface ozone air quality will be studied under the high emission \gls{ssp}~5. \gls{odina} will also enable the research team to study ozone impacts through vegetation on the global carbon cycle and water cycle, and thus ultimately climate.
The \gls{odina} project is guided by \textbf{five working hypotheses}: 

\begin{enumerate}
\itemsep0pt
\item Elevated ozone concentrations affect plant physiology via a reduction of the maximum electron transport rate and maximum carboxylation efficiency and a subsequent decreased stomatal conductance and photosynthesis. 
\item Reduced stomatal conductance will decrease ozone uptake by vegetation and hence diminish the dry deposition sink of ozone to the land biosphere. This will in turn act as a positive feedback increasing ground-level ozone concentrations in regions with damaged vegetation and thus degrading ambient air quality.
\item Decreasing stomatal conductance will further affect transpiration of plants implicating lower relative humidity and less cooling by latent heat. At the same time more water will remain in the soil.
\item A reduction of photosynthesis will affect the carbon sequestration and the terrestrial carbon sink, and hence diminish the removal of \ch{CO_2} from the atmosphere.
\item All described feedback mechanisms may increase surface air temperature and thus amplify local/regional temperature extremes.
\end{enumerate}

Guided by these hypotheses, the project team will specifically:
\begin{enumerate}
\itemsep0pt
\item Investigate the interaction between ozone and plant physiology and quantify on the one hand the degree of plant damage expected by elevated ozone concentrations, and on the other the anticipated increase in ozone burden due to a reduced dry deposition.
\item Quantify the effect of plant health on \gls{bvoc} emissions and subsequent effects on air quality.
\item Quantify the effect of reduced stomatal conductance and photosynthesis on carbon sequestration and \gls{et}, and thus indirect impacts of ozone on the climate forcing.
\end{enumerate}

